---
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# dangeo

## Overview

Package to access to the Map Supply Download via the kortforsyningen FTP. You would need to create an account on [kortforsyningen](https://www.kortforsyningen.dk/indhold/min-side-0).

## Installation

```{r, eval = FALSE}

if (!require("remotes")) install.packages("remotes")
remotes::install_github("javiereliomedina/dangeo")

```

## Usage

```{r lbr, message = FALSE}
  
library(dangeo) 
 
```

First we would need to set our Username (kortforsyningen_id = "XXX") and Password (kortforsyningen_pwd = "XXX") on *.Renviron*.

```{r user}

# usethis::edit_r_environ()  # Open .Renviron file, and save the username and password
set_user <- paste(Sys.getenv("kortforsyningen_id"), Sys.getenv("kortforsyningen_pwd"), sep = ":" )

```

Then we can download a ".zip" file (e.g. *DK_CORINE_SHP_UTM32-WGS84.zip*) in our local directory by calling the function *dangeo_get_data()*. By default the local directory is defined as *out_folder = rappdirs::user_cache_dir()* but we can change it (*out_folder = "./local/path"*). The file will not be downloaded if it already exist in the folder, but we can overwrite it by setting *overwrite = TRUE*.

```{r get_data}

dangeo_get_data(ftp_folder = "CORINE",
                zip_name   = "DK_CORINE_SHP_UTM32-WGS84.zip")

```
