---
output:
  github_document:
    html_preview: false
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# dangeo

## Overview

Package to access to the Map Supply Download via the kortforsyningen FTP. You would need to create an account on [kortforsyningen](https://www.kortforsyningen.dk/indhold/min-side-0).

## Installation

```{r, eval = FALSE}

if (!require("remotes")) install.packages("remotes")
remotes::install_github("javiereliomedina/dangeo")

```

## Usage

```{r lbr, message = FALSE}
  
library(dangeo) 
 
```

First we would need to define the username and the password for kortforsyningen, and the local directory where the files will be downloaded (i.e. *dangeo_set_param()*). By default *dangeo* looks for credentials on *.Renviron* (kortforsyningen_id = "username" and kortforsyningen_pwd = "password"), and the local directory is defined as *dangeo_set_param(loc_dir = rappdirs::user_cache_dir())*, although it can be changed (*dangeo_set_param(loc_dir = "./local/path")*).  

```{r set-param}

# usethis::edit_r_environ()  # Open .Renviron file, and save the username (kortforsyningen_id = "username") and password (kortforsyningen_pwd = "password")

dangeo_set_param()

```

Then we can download a ".zip" file (e.g. *DK_CORINE_SHP_UTM32-WGS84.zip*) in our local directory by calling the function *dangeo_get_data()*. The file will not be downloaded if it is already in the local directory, but we can overwrite it by setting *overwrite = TRUE*.

```{r download-data}

dangeo_get_data(ftp_folder = "CORINE",
                zip_name   = "DK_CORINE_SHP_UTM32-WGS84.zip")

```
